Random number generation and applications on GPU’s in R?

### 2021-10-02 pkg/gpuRandom/inst/documents/paper1_2021_5/paper1.Rnw
streams
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@2887 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

check reproducibility
<<simStuff, eval=TRUE,tidy=TRUE>>=
c(as.vector(sim_2), as.vector(gpuRandom::runif(n=6, streams=myStreamsGpu1, Nglobal=c(1,nrow(myStreamsGpu1)), type = "double")))
as.vector(gpuRandom::runif(n=12, streams=vclMatrix(myStreamsCpu), Nglobal=c(1,nrow(myStreamsGpu1)), type = "double"))
@

>>>>

check reproducibility
<<simStuff, eval=TRUE,tidy=TRUE>>=
as.vector(gpuRandom::runif(n=4, streams=myStreamsGpu1, Nglobal=c(1,nrow(myStreamsGpu1)), type = "double"))
as.vector(gpuRandom::runif(n=10, streams=myStreamsGpu2, Nglobal=c(1,nrow(myStreamsGpu1)), type = "double"))[-(1:6)]
@
